Integration of national demographic-disturbance relationships into local caribou population viability projections can reduce uncertainty and inform monitoring decisions

### 2024-10-16 analysis/paper/paper.Rmd
add supp mat captions

>>>>

# Supplementary material
Supplement A: Definitions of variables and parameters in the Bayesian population model
Supplement B: Model of bias in recruitment estimates from calf:cow surveys
Supplement C: Calibration of priors
Supplement D: Alternative disturbance and monitoring scenarios
Supplement E: Expected value of perfect information
Supplement F: Sensitivity to unknown bias in recruitment estimates from calf:cow surveys
